Constrained Optimization-Based Neuro‒Adaptive Control (CoNAC) for Uncertain Euler‒Lagrange Systems Under Weight and Input Constraints

### 2025-02-14 main.tex
Add public

\documentclass[lettersize,journal]{IEEEtran}
% code
% MY PACKAGES ===================================
\usepackage{epsfig}
\usepackage{lipsum}  
\usepackage{kotex}
% \usepackage{natbib}
\usepackage{cite}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{enumitem}
\newlist{steps}{enumerate}{1}
\setlist[steps, 1]{label = Step \arabic*: }
\usepackage{hyperref}
\hypersetup{
    linkbordercolor=blue,
    filebordercolor=red,
    citebordercolor = green,      
    urlbordercolor=red,
    %
    % colorlinks=true,
    % linkcolor=blue,
    % filecolor=blue,
    % citecolor = blue,      
    % urlcolor=cyan,
 }
 \usepackage{algorithm}
 \usepackage{svg}

\usepackage{amsmath,amsfonts}
\usepackage{algorithmic}
\usepackage{array}
% \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\usepackage{subfig}
\usepackage{textcomp}
\usepackage{stfloats}
\usepackage{url}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{multicol}

@@

\begin{figure*}[!t]
    \centering
    \includegraphics[width=0.7\linewidth]{Controller.drawio.png}
    % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
    \caption{Architecture of the constrained optimization-based neuro‒adaptive controller (CoNAC).}
    \label{fig: controller}
\end{figure*}

@@

% **********************************************************
% SYSTEM FIGURE AND TABLE
\begin{figure}[!t]
    \centering
    \includegraphics[width=0.7\linewidth]{RobotModel.drawio.png}
    \caption{Two-link manipulator model.}
    \label{fig: manipulator}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=0.9\linewidth]{fig13.eps}
    \caption{Effect of parameter $p$ in the control input saturation function $h$ and boundedness of $\Vert\partial h/\partial \tau\Vert_F$.}
    \label{fig: h func}
\end{figure}

@@

% **********************************************************
% SIMULATION FIGURES
\begin{figure*}[!t]
    \centering
        \subfloat[BSC]{\includegraphics[width=0.49\linewidth]{fig1.eps}%
        \label{fig: tracking_CM1}}
    \hfill
        \subfloat[DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig2.eps}%
        \label{fig: tracking_CM2}}
    \vfill
        \subfloat[DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig3.eps}%
        \label{fig: tracking_CM3}}
    \hfill
        \subfloat[CoNAC]{\includegraphics[width=0.49\linewidth]{fig4.eps}%
        \label{fig: tracking_CoNAC}}
    \caption{Comparison of the tracking performance across the selected controllers.}
    \label{fig: tracking}
\end{figure*}

\begin{figure*}[!t]
    \centering
        \subfloat[BSC]{\includegraphics[width=0.49\linewidth]{fig5.eps}%
        \label{fig: control_CM1}}
    \hfill
        \subfloat[DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig6.eps}%
        \label{fig: control_CM2}}
    \vfill
        \subfloat[DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig7.eps}%
        \label{fig: control_CM3}}
    \hfill
        \subfloat[CoNAC]{\includegraphics[width=0.49\linewidth]{fig8.eps}%
        \label{fig: control_CoNAC}}
    \caption{Comparison of the control input $\tau$ and the physically saturated control input $h(\tau)$ across the selected controllers.}
    \label{fig: control}
\end{figure*}

\begin{figure}[!t]
    \centering
    {\includegraphics[width=0.9\linewidth]{fig16.eps}
    \caption{Control input paths of DNN-BSC and CoNAC during the time interval from 5 s to 8 s.}
    \label{fig: ball control}}
\end{figure}

\begin{figure*}[!t]
    \centering
        \subfloat[Multipliers of CoNAC]{\includegraphics[width=0.49\linewidth]{fig12.eps}%
        \label{fig: multiplier_CoNAC}}
    \hfill
        \subfloat[Weight norms of DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig9.eps}%
        \label{fig: weight_CM2}}
    \vfill
        \subfloat[Weight norms of DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig10.eps}%
        \label{fig: weight_CM3}}
    \hfill
        \subfloat[Weight norms of CoNAC]{\includegraphics[width=0.49\linewidth]{fig11.eps}%
        \label{fig: weight_CoNAC}}       
    \caption{Lagrange multipliers of CoNAC and weight norms of DNN-BSC, DNN-BSC-A, and CoNAC.}
    \label{fig: weight and multiplier}
\end{figure*}
% SIMULATION FIGURES
% **********************************************************

@@

%  SECTION APPENDIX ======================================
%  \appendices

% \section{Proof of Lemma \ref{lem1}}\label{sec:proof lem1}

% Let $\omega^*\triangleq [\theta_k^{*T}; [\hat\theta_i]_{i\in[0,\cdots,k-1]}]$ and $\hat\omega\triangleq [\hat\theta_k^{T}; [\hat\theta_i]_{i\in[0,\cdots,k-1]}]$. 
% If the Assumption \ref{assum1} holds (i.e., $c(\omega^*)<0,c(\hat\omega)\ge 0$), then $\nabla c_{j,k}^T\hat\theta_k>0$ also implies $\nabla c_{j,k}^T\tilde\theta_k>0$, as demonstrated by the following analysis: 
% \begin{equation}
%     \begin{aligned}
%         -\nabla c_{j,k}^T \tilde\theta_k=&\nabla c_{j,k}^T(\theta_k^*-\hat\theta_k)
%         =
%         {d\over d\delta } c_j(\hat\omega +\delta (\omega^*-\hat\omega))\bigg\vert _{\delta=0} \\
%         =& \lim_{\delta\to 0} {c_j(\hat\theta-\delta(\omega^*-\hat\omega)) + c_j(\hat\omega)\over \delta}\\
%         \le& \lim_{\delta\to0} {\delta c_j(\omega^*) + (1-\delta) c_j(\hat\omega)-c_j(\hat\omega)\over \delta}
%         \\
%         =& c_j(\omega^*) - c_j(\hat\omega) < 0
%         \end{aligned}
% \end{equation}

% It follows that $\nabla c_{j,k}^T\hat\theta_k>0$ holds for all the constraints introduced in Section \ref{sec:cstr candidates}.

% \section{Details of CM3}\label{sec:detail CM3}

% As motivated by 
% \color{red}
% \cite{RN111}-\cite{RN110}
% \color{black}
% , the auxiliary system is introduced to compensate the control input saturation, as
% \begin{equation}
%     \dot \zeta  = 
%     \begin{cases}
%         -K_\zeta \zeta - 
%         \bigg({
%         \vert {\tilde z}^TM_0^{-1}k_\zeta\Delta\tau\vert +0.5k_\zeta^2\Delta \tau^T\Delta \tau
%         \over
%         \Vert\zeta\Vert^2
%         }\bigg)
%         \zeta
%         +
%         k_\zeta
%         \Delta \tau,
%         \\
%         \quad\quad\quad
%         \quad\quad\quad
%         \quad\quad\quad
%         \quad\quad\quad
%         \quad\quad\quad\quad

%         \Vert \zeta\Vert \ge \mu
%         \\
%         -K_\zeta \zeta+ k_\zeta\Delta \tau, 
%         \quad\quad\quad
%         \quad\quad\quad
%         \quad\quad\quad\ 
%         \Vert\zeta\Vert < \mu
%     \end{cases}
%     \label{eq. aux system}
% \end{equation}
% where $\zeta$ denotes the auxiliary state variables, $\Delta\tau \triangleq h(\tau) - \tau$, $\mu\in\mathbb R_{>0}$ is a positive constant, and $K_\zeta=K_\zeta^T>0$.
% To scale the difference of the magnitude between ${\tilde z}$ and $\Delta\tau$, $k_\zeta\in\mathbb R_{>0}$ is used.

% Let the control law be defined as 
% \begin{equation}
%     \tau =-{k_z}M_0{\tilde z}-M_0K_p \zeta -M_0{\tilde q}+C_0{z}+G_0-\hat f+M_0 \dot {z^*}
%     \label{eq: control law CM3}
% \end{equation}
% where $K_p$ denotes the gain matrix.
% Then the system is bounded with the following criteria: ${k_q} > 0, {k_z} >1/2, k_\zeta>1, \mu>1, K_p > 0, K_\zeta >{1\over 2}(K_p^TK_p+I),\dot{\hat\theta } = \text{Proj}_{\Omega}[\alpha\nabla\hat\Phi^T{M^{-1}}^{T} {\tilde z}]$.
% The proof of the boundedness can be readily obtained using the Lyapunov function $V=(1/2){\tilde q}^T{\tilde q}+(1/2){\tilde z}^T{\tilde z}+(1/2\alpha)\tilde\theta^T\tilde\theta + (1/2)\zeta^T\zeta$.

>>>>

\documentclass[lettersize,journal]{IEEEtran}
% code

\input{dding_template/tex_packages/tex_packages_general.tex}

@@

\begin{figure*}[!t]
    \centering
    \includegraphics[width=0.7\linewidth]{fig/Controller.drawio.png}
    % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
    \caption{Architecture of the constrained optimization-based neuro‒adaptive controller (CoNAC).}
    \label{fig: controller}
\end{figure*}

@@

% **********************************************************
% SYSTEM FIGURE AND TABLE
\begin{figure}[!t]
    \centering
    \includegraphics[width=0.7\linewidth]{fig/RobotModel.drawio.png}
    \caption{Two-link manipulator model.}
    \label{fig: manipulator}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=0.9\linewidth]{fig/fig13.eps}
    \caption{Effect of parameter $p$ in the control input saturation function $h$ and boundedness of $\Vert\partial h/\partial \tau\Vert_F$.}
    \label{fig: h func}
\end{figure}

@@

% **********************************************************
% SIMULATION FIGURES
\begin{figure*}[!t]
    \centering
        \subfloat[BSC]{\includegraphics[width=0.49\linewidth]{fig/fig1.eps}%
        \label{fig: tracking_CM1}}
    \hfill
        \subfloat[DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig/fig2.eps}%
        \label{fig: tracking_CM2}}
    \vfill
        \subfloat[DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig/fig3.eps}%
        \label{fig: tracking_CM3}}
    \hfill
        \subfloat[CoNAC]{\includegraphics[width=0.49\linewidth]{fig/fig4.eps}%
        \label{fig: tracking_CoNAC}}
    \caption{Comparison of the tracking performance across the selected controllers.}
    \label{fig: tracking}
\end{figure*}

\begin{figure*}[!t]
    \centering
        \subfloat[BSC]{\includegraphics[width=0.49\linewidth]{fig/fig5.eps}%
        \label{fig: control_CM1}}
    \hfill
        \subfloat[DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig/fig6.eps}%
        \label{fig: control_CM2}}
    \vfill
        \subfloat[DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig/fig7.eps}%
        \label{fig: control_CM3}}
    \hfill
        \subfloat[CoNAC]{\includegraphics[width=0.49\linewidth]{fig/fig8.eps}%
        \label{fig: control_CoNAC}}
    \caption{Comparison of the control input $\tau$ and the physically saturated control input $h(\tau)$ across the selected controllers.}
    \label{fig: control}
\end{figure*}

\begin{figure}[!t]
    \centering
    {\includegraphics[width=0.9\linewidth]{fig/fig16.eps}
    \caption{Control input paths of DNN-BSC and CoNAC during the time interval from 5 s to 8 s.}
    \label{fig: ball control}}
\end{figure}

\begin{figure*}[!t]
    \centering
        \subfloat[Multipliers of CoNAC]{\includegraphics[width=0.49\linewidth]{fig/fig12.eps}%
        \label{fig: multiplier_CoNAC}}
    \hfill
        \subfloat[Weight norms of DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig/fig9.eps}%
        \label{fig: weight_CM2}}
    \vfill
        \subfloat[Weight norms of DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig/fig10.eps}%
        \label{fig: weight_CM3}}
    \hfill
        \subfloat[Weight norms of CoNAC]{\includegraphics[width=0.49\linewidth]{fig/fig11.eps}%
        \label{fig: weight_CoNAC}}       
    \caption{Lagrange multipliers of CoNAC and weight norms of DNN-BSC, DNN-BSC-A, and CoNAC.}
    \label{fig: weight and multiplier}
\end{figure*}
% SIMULATION FIGURES
% **********************************************************

@@
